On the presentation of orthogonal groups over polynomial rings

### 2019-05-18 dl-paper.tex
Written down formulas deducing the claim for orthogonal roots

Let us show that F3 and F4 hold automatically.
Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
Then 
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
\end{comment}
\printbibliography
\end{document}

>>>>

Let us show that F3 and F4 hold automatically.
Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
Then 
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
\end{comment}
\begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta}(b'X^{-1}), {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$3_1$ for sharp angles}\\
 = [[x_{-\beta-\gamma}(b''), x_\gamma(X^{-1})], {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta-\gamma}(b''), [x_\gamma(X^{-1}), x_{\alpha+\beta}(1)]] & \text{ by R$3_0$}\\
 = x_{\alpha}(b'''X^{-1}) & \text{ by R$2_1$.} \end{align*}

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}

\printbibliography
\end{document}
